Bayesian statistics and swine flu

### 2009-08-12 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@357 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\documentclass{beamer}
\usepackage[nogin]{Sweave}
\title{Bayesian statistics and  swine flu}
\author{Patrick Brown$^1$,  Peter Neal$^2$}
\institute{1:Cancer Care Ontario and Dalla Lana School of Public Health, University of Toronto; 2: School of Mathematics, University of Manchester} 
\usepackage{amsmath,subfigure}

@@

\begin{frame}[fragile]
\frametitle{What we need}
\input{bayesPandemicPriors.txt}
\end{frame}

@@

\begin{frame}
\frametitle{}
\begin{block}{trace plots}
<<tracePlot>>=
plot(paramSample[,"probs.D"], type="l")
@
\end{block}

>>>>

\documentclass{beamer}
\usepackage[nogin]{Sweave}
\title{Bayesian statistics and  swine flu}
\author{Patrick Brown$^1$,  Peter Neal$^2$}
\institute{1:Cancer Care Ontario and Dalla Lana School of Public Health, University of Toronto; 2: School of Mathematics, University of Manchester} 
\usepackage{amsmath,subfigure,alltt}

@@

\begin{frame}[fragile]
\frametitle{What we need}
\begin{alltt}
\input{bayesPandemicPriors.txt}
\end{alltt}
\end{frame}

@@

\begin{frame}
\frametitle{Fatality probability}
\begin{columns}
\column{0.5\textwidth}
\begin{block}{trace plots}
<<tracePlot,fig=true>>=
plot(paramSample[,"probs.D"], type="l")
abline(h=params$probs["D"], col="red")
@
\end{block}
\column{0.5\textwidth}

\begin{block}{Histogram}
<<histPost>>=
hist(paramSample[,"probs.D"], breaks=12)
abline(v=params$probs["D"], col="red")
@
\end{block}
\end{columns}
\end{frame}
\end{document}
